\documentclass{article}
\usepackage[utf8]{inputenc}

\title{Alpha: Progress Report}
\author{Mike Fang\\ mf647 \and Andrei Shpilenok\\ ais76}

\begin{document}
\maketitle
\section*{Vision}
Our vision of unifying content and styling natively has not
changed with this sprint. Our goal is to develop a fully fleshed out language
for the web which brings together CSS and HTML and absolves
javascript of the responsibility of having to do everything. We also aim to improve 
styling in the web by integrating constraints with our language. We envision the
project to consist of two main parts:
\begin{enumerate}
	\item Designing and Parsing the Language
	\item Creating a Dummy Browser to Display the Result of the Language
\end{enumerate}

\section*{Progress}

We have made significant progress on designing and parsing the language this sprint.
We laid out the specification for the language, and finished implementing 
key components of the parser.

In order to implement the parser, we used a parser generator library, rust-peg.
The natural language 
specification of the language was transformed into an
intermediary grammer, parsing expression grammer(PEG), and then fed into the parser
generator. With the parser from the generator, we can then feed our language into it
to generate the appropriate data for the browser to paint with.

Because of the syntactical and semantic differences between the styling portion and 
the markup portion of our langauge, we built two parsers to handle them. The parsers
also output different data structures. In our demo, we are inputting two realistic
examples, one for the styling portion and one for the markup portion,
and printing out the output of the parsers. This demonstrates the efficacy of
our parsers and shows that we will be able to take the next step of transforming
parser output to information the browser can use to paint with.

\section*{Activity}

\subsection*{Andrei}
\begin{enumerate}
	\item Designed the core features of the language
	\item Wrote the parsers
	\item Wrote the blog post
\end{enumerate}

\subsection*{Mike}
\begin{enumerate}
	\item Provided feedback on the core features of the langauge
	\item Wrote the Progress Report
	\item Wrote test cases for the parsers and fixed any issues identified from 
	      testing
\end{enumerate}

\section*{Productivity}
We have been very productive this sprint and
accomplished the two main tasks of designing core features of the language
and writing the parser. We established a strong base for the next phase of the project
. In our charter, we were more ambitious about what we could accomplish this sprint,
but after starting, we realized having a strong design and being able to parse the
language was more than enough work and would take a lot longer than anticipated.

\section*{Grade}

We believe we achieved our goals for this sprint and achieved an excellent scope
grade. The bulk of our work this phase was doing research on packages and language
ideas so that we had a solid plan in place for what features we wanted to implement
and how to implement them. We spent the rest of our time working on the 
parser--translating our language to PEG, translating the PEG to input for the parser, and testing our parser thoroughly. 
This is comparable in scope to any of the programming
projects we had to do in class. 

\section*{Goals}

\subsection*{Satisfactory}
\begin{enumerate}
	\item Combining the two parsers so that we can process a complete program
	\item Implement bundle parsing in the styling portion of the language
\end{enumerate}

\subsection*{Good}
\begin{enumerate}
	\item Have an end-to-end implementation with a dummy browser which can receive
		our language as input and output a web page with basic formatting
	\item Users will be able to use pre-implemented tags in the code to structure
		data
\end{enumerate}

\subsection*{Excellent}
\begin{enumerate}
	\item Users will be able to create custom tags
	\item Users will be able to use functions and variables 
		in the styling portion of the language to structure and
		style data
\end{enumerate}
\end{document}
